---
title: "Package Overview"
author: "Dylan Stark"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## General Use

```{r echo=FALSE}
library(pickacs)
```

```{r echo=FALSE}
# Load sample data for this vignette
data("child_poverty_cook_2013_5yr")
acs_data <- child_poverty_cook_2013_5yr
```

Pull data from ACS using `fetch_acs_data`.
This will use the [acs package](https://cran.r-project.org/web/packages/acs/index.html) to retrive all data for the specified construction (`constr`).

```r
library(acs)
library(pickacs)

geo <- geo.make(state = "IL", county = "Cook", tract = "*") 
endyear <- 2013
span <- 5

acs_data <- fetch_acs_data("Child Poverty", geo, endyear, span)
```

Construct child poverty measures.

```{r}
cp <- construct("Child Poverty", data = acs_data)
```

Use new measures for good.

```{r}
library(ggplot2)

ggplot(cp$data, aes(x = nPov_ALt5)) + geom_bar()
```

## Development

The easiest way to get started working on the package is to [open up the `pickacs.Rproj` project in RStudio](http://r-pkgs.had.co.nz/package.html#projects).
Once in RStudio, you can [load the source](http://r-pkgs.had.co.nz/r.html#r-workflow).

```
> devtools::load_all(".")
Loading pickacs
Behold, ACS Constructicons!
1.    Child Poverty
```

After loading you can build the vignettes with `devtools::build_vignettes()` and [test the code](http://r-pkgs.had.co.nz/tests.html) with Ctrl/Cmd + Shift + T.

## Adding Measures

Adding new measures is (relatively) easy when using `R/msr_child_poverty.R` as a template.
Let's say we want to add some educational attainment measures.
First, we make a copy of the child poverty file as something like `R/msr/edu_attain.R`.
Next, we update the *class name* from `child_poverty` to `edu_attain`, and *full name* from "Child Poverty" to "Educational Attainment".
We also update the target ACS table from "B17006" to "B15001".
This will give us the following updated methods:

```r
register.edu_attain <- function(obj) {
    constr_register("Educational Attainment",
                    class_name = "edu_attain",
                    tables = "B15001")
}

measure.edu_attain <- function(constr) {
    message("Constructing ", constr$name, " measures")

    new_data <- compute_measure(orig_data = constr$data)

    constr$data <- cbind(constr$data, new_data)

    constr
}
```

Finally, we reimplement `compute_measure` so that it creates the extra variables we need.
The basic idea here is that this method takes a data frame of ACS data (see General Use section for overview of how to get that) and returns a data frame with one new measurement per column.
Once you've implemented this method, you're all done.
You can now reload the package and start using your new measure:

```
> devtools::load_all(".")
Loading pickacs
Behold, ACS Constructicons!
1.    Child Poverty
2.    Educational Attainment
> edu_data <- fetch_acs_data("Educational Attainment", geo, endyear, span)
> ed <- construct("Educational Attainment", data = edu_data)
```

## Encoding Variables

This package includes coded ACS variable data for all 1, 3, and 5-year surveys.
The `data-raw/codes.csv` table defines variable encodings.
The `data-raw/variables.R` script creates mappings from encoded variable names to original variable names.
And, `data-raw/update_sysdata.R` stores the encoded variable mappings within the package for easy distribution.

If any of these files are updated, run `data-raw/update_sysdata.R` to regenerate the internal data set (stored in `R/sysdata.R`).

```
> source("data-raw/update_sysdata.R")
```
